Technical Report

### 2018-06-18 fully-abstract-comp/technical-report.tex
Remove obsolete TODOs.

\section{Full Abstraction}
\label{sec:full-abstraction}
\lau{TODOs from last day in Leuven}
\lau{RESOLVED: components have optional main (pc/data pair)}
\lau{RESOLVED: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{RESOLVED?: Component logical relation. Rough sketch is in white-board-notes/leuven-23-3-2018-3.jpg (top left).}
\dominique{RESOLVED: Compatibility lemma for linking: if $c_1$ and $c_1'$ are related and $c_2$ and $c_2'$, then so should be $c_1\bowtie c_2$ and $c_1' \bowtie c_2'$ (if defined).}
\lau{RESOLVED: Version of FTLR for programs.}
\lau{RESOLVED: Compatibility lemma for initial executable configuration construct, i.e. a lemma that says ``if two programs are related, then their initial executable configurations will be related''.}
\lau{RESOLVED: A logical relation for executable configurations.}
\lau{RESOLVED: contextual equivalence should be defined in terms of initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}

>>>>

\section{Full Abstraction}
\label{sec:full-abstraction}
\lau{TODOs from last day in Leuven}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
